Tor's Usability for Censorship Circumvention

### 2015-12-11 paper/circumvention-experiment.tex
Fix references to figures
In-line references to figures used to refer to the wrong ones when compiled.
(e.g., it would refer to Figure 6 when actually the figure in question was 10)

This was fixed by changing the placement of the \label command within
the figure environment: it's now after the \caption command.
This matters because of how the \label macro is defined.
See: https://tex.stackexchange.com/a/111281
my changes

\begin{abstract}
Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor \cite{whotor}.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration interface of Tor Browser,
as censorship circumvention requires correct transport configurations.
We will conduct a large-scale user study examining how 60-100 users
navigate Tor's configuration wizard to complete typical browsing tasks
in three different adversarial settings. Our study combines quantitative measurements (interface
paths taken to success, time to success, and which configuration was chosen) and
qualitative measurements (if users were comfortable with use, what was most confusing, and 
if they would use the browser again). The first phase of the study evaluated if and how
easily users can circumvent censorship using Tor Browser. The second phase
of the study will test the improvements to the interface. 
Our goal is to integrate positive usability changes into the Tor Browser. Since
the configuration interface is modular and does not require changes to the Tor Browser
functionality, these changes will be easy to deploy.

@@

\begin{figure}[h]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface.}
\end{figure}

@@

After users complete the browsing tasks (or time runs out), we conduct an
interview, collecting qualitative feedback from
participants about their browsing experience as a whole
and the configuration interface specifically.
We ask questions such as
``What was the most challenging part of connecting?''
and
``What is one change you would recommend?''

\subsection{Interface design and iteration}
After completing the qualitative user studies, we analyzed their results to
identify common themes and problems. Based on these, we then designed
improvements to the Tor launcher interface.

To do this, we used an iterative design process, starting with low-fidelity
(paper and pencil) prototypes and then proceeding to higher-fidelity versions.
At each stage, the prototype was clickable, allowing for more realistic
simulation.

We collected feedback from researchers, professors, and Tor users and developers
through the Tor project's mailing lists. We then iterated on the design by
incorporating the comments and suggestions we received into the next version of
the interface.

\subsection{Quantitative evaluation of improvements}
Once the new design of the user interface is finalized, we will conduct a
large-scale quantitative evaluation, to test whether the improvements had a
measurable effect on people's ability to connect to the Tor network.

The experimental procedure will be nearly identical to the procedure for the
qualitative portion of the study, described above. However, rather than
conducting open-ended interviews at the end of the tasks, participants will be
asked to fill out a brief survey. Furthermore, the interface will be
instrumented to collect metrics and statistics for use in analysis and
hypothesis testing.
Some examples of metrics collected include the time spent on each screen, which
paths the user followed, which interface elements they interacted with, and how
often they did so. These will be analyzed in conjunction with high-level metrics
(was the user able to connect to Tor successfully?).

@@

The qualitative interface evaluation yielded hours of observations, as well as
interview data, for a set of 16 pre-selected, diverse participants taking
various UI paths in different simulated censorship environments. This section
discusses the insights gathered from the qualitative interface evaluation, which
has shaped the re-design of the interface. All of the results are grounded in
participants' experiences and feedback, which are available publicly online. The
video screen captures from the experiment can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{here};
a summary of each video can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{here}.
The corresponding notes from the after-experiment interview can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{here}.

@@

\begin{figure}[h]
\label{fig:redesign-proxy}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-proxy.png}
    \caption{the proxy configuration screen, with an option to automatically
        ``Import from another browser''}
\end{figure}

@@

\begin{figure}[h]
\label{fig:redesign-noproxy}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-noproxy.png}
    \caption{The default option is now to ``Proceed without proxy settings.''}
\end{figure}

@@

\begin{figure}[h]
\label{fig:redesign-firstscreen}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-firstscreen.png}
    \caption{the initial connection screen. Note the prominence given to the
    ``Connect'' button.}
\end{figure}

@@

\begin{figure}[h]
\label{fig:redesign-bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
    \caption{the bridge selection screen, with the option to ``Add Custom
    Bridge''}
\end{figure}

A progress indicator at the top of the window indicates which configuration step
the user is on. It serves to clarify the independence of bridges and proxies,
which need to be configured separately. In the event of a failure, the user is
returned to the first step of the process -- the bridge configuration -- to
avoid misleading users into thinking the proxy settings are the culprit. Previously,
the user had to manually click to go backward in the dialog to configure bridges.
Even in the rare event that the proxy is the issue for the connection setting, the user
will be directed to the proxy page naturally through the flow of the UI. \\

@@

Many users were led astray by interface elements that were unhelpful or
misleading if the program encountered connection problems. Our design seeks to
prevent such confusion by anticipating failures and providing specific instructions
for our participants on their next steps.

@@

\begin{figure}[h]
\label{fig:redesign-waiting}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-waiting.png}
    \caption{the new connection screen}
\end{figure}

@@

\begin{figure}[h]
\label{fig:redesign-failure}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-failure.png}
    \caption{the screen displayed when a connection failed}
\end{figure}

>>>>

\begin{abstract}
Tor has grown beyond its original purpose as an anonymity tool and has 
since become an important censorship circumvention tool. It is now listed
as one of the ways that normal people use Tor \cite{whotor}.
We specifically examine its usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration interface of Tor Browser,
as censorship circumvention requires correct transport configurations.
The first phase of the study evaluated if and how easily users can circumvent censorship 
using Tor Browser; the results of conducting our experiment and the interface redesign
is presented in this paper. The second phase
of the study will test the improvements to the interface, which has yet to happen. However, we take
some time to describe our plans. 
Our goal is to integrate positive usability changes into the Tor Browser, making
censorship circumvention an easier process for users around the world.

@@

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface.}
\end{figure}

@@

After users complete the browsing tasks (or time runs out), we conducted an
interview asking participants about their censorship circumvention experience.
We were able to tailor the interview to the particular participant, since we were able to
observe our participants' sessions. This way, we could follow up and ask participants
about reasons for taking particular actions and verify any hypothesis we had about 
the participant (such as ``they didn't know what to do on window 3'').  We did
ask a couple question across all participants: 
``What was the most challenging part of connecting?''
and
``What is one change you would recommend?''

\subsection{Interface design and iteration}
After completing the qualitative user studies, we analyzed the results to
identify common themes and problems. These were the basis of our interface 
redesign. To do this, we used an iterative design process, starting with low-fidelity
(paper and pencil) prototypes and then proceeding to higher-fidelity (realistic clickable mockups)
prototypes.We collected feedback from researchers, professors, and Tor users and developers
through the Tor project's mailing lists. We then iterated on the design by
incorporating the comments and suggestions we received into the next version of
the interface. We plan to take some qualitative measurements of the new design
by having some participants think aloud while they use our realistic mockup. This is 
to get any feedback before we launch our quantitative interface evaluation.

\subsection{Quantitative interface evaluation}
Once the new design of the user interface is finalized, we will conduct a
large-scale quantitative evaluation, to test whether the improvements had a
measurable effect on people's ability to connect to the Tor network.

The experimental procedure will be nearly identical to the procedure for the
qualitative portion of the study, described above. However, rather than
conducting open-ended interviews at the end of the tasks, participants will be
asked to fill out a brief survey. Furthermore, the interface will be
instrumented to collect metrics and statistics for use in analysis and
hypothesis testing. Such metrics include the time spent on each screen, which
paths were taken, which interface elements were interacted with, etc.

@@

The qualitative interface evaluation yielded hours of observations and
interview data, for a set of 16 pre-selected, diverse participants taking
various UI paths in different simulated censorship environments. This section
discusses the insights gathered from the qualitative interface evaluation, which
has shaped the re-design of the interface. All of the results are grounded in
participants' experiences and feedback, which are available publicly online. The
video screen captures from the experiment can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{here};
a summary of each video can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{here}.
The corresponding notes from the after-experiment interview can be found
\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{here}.

@@

\begin{figure}[t]
\label{fig:redesign-proxy}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-proxy.png}
    \caption{the proxy configuration screen, with an option to automatically
        ``Import from another browser''}
\end{figure}

@@

\begin{figure}[t]
\label{fig:redesign-noproxy}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-noproxy.png}
    \caption{The default option is now to ``Proceed without proxy settings.''}
\end{figure}

@@

\begin{figure}[t]
\label{fig:redesign-firstscreen}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-firstscreen.png}
    \caption{the initial connection screen. Note the prominence given to the
    ``Connect'' button.}
\end{figure}

@@

\begin{figure}[t]
\label{fig:redesign-bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
    \caption{the bridge selection screen, with the option to ``Add Custom
    Bridge''}
\end{figure}

A progress indicator at the top of the window indicates various steps necessary
for configuring a connection. In addition to communicating to the user what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately. In the event of a failure, the user is
returned to the first step of the process -- the bridge configuration -- to
avoid misleading users into thinking the proxy settings are the culprit. Previously,
the user had to manually click to go backward in the dialog to configure bridges.
Even in the rare event that the proxy is the issue for the connection setting, the user
will be directed to the proxy page naturally through the flow of the UI. \\

@@

Users were led astray by interface elements that were unhelpful or
misleading if the program encountered connection problems. Our design seeks to
prevent such confusion by anticipating failures and providing specific instructions
for our participants on their next steps.

@@

\begin{figure}[t]
\label{fig:redesign-waiting}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-waiting.png}
    \caption{the new connection screen}
\end{figure}

@@

\begin{figure}[t]
\label{fig:redesign-failure}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-failure.png}
    \caption{the screen displayed when a connection failed}
\end{figure}
